### 2018-11-07 articleSFDS.tex
réponse au relecteur 2 pour l'indépendance des erreurs

\begin{eqnarray}
\mathcal{M}_2 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i} &=& F(\boldsymbol{x}_i,\boldsymbol{\theta}) + \epsilon_i,
\label{eq:M2}\\
F(\bullet,\bullet) & \sim &{\mathcal{GP}}{\Big(m_S(\bullet,\bullet),c_S\{(\bullet,\bullet),(\bullet,\bullet)\}\Big)},
\nonumber
\end{eqnarray}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$ and the random function $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ stands for a Gaussian process (GP) over the joint domain of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. Its mean function $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ is generally a linear form of simple functions of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. Its covariance function $c_S\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}=\sigma_S^2 r_{\boldsymbol{\psi}_S}\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}$ is such as the function $r_{\boldsymbol{\psi_S}}\{(\bullet,\bullet),(\bullet,\bullet)\}$ is the correlation function with a vector parameter $\boldsymbol{\psi}_S$. This parameter vector represents the scale and the regularity of the kernel and where $\sigma_S^2$ represents the variance. The mean $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ can be written as\newline

@@

where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$, and $\delta(\bullet)$ stands for a Gaussian process which mimics the discrepancy and will only depends on the input variables $\boldsymbol{x}$. We can write $\delta(\bullet)\sim\mathcal{GP}(\boldsymbol{m}_{\delta}(\bullet),c_{\delta}(\bullet,\bullet))$ with $\forall \boldsymbol{x}, \ \boldsymbol{m}_{\delta}(\boldsymbol{x})={\boldsymbol{h}_{\delta}}(\boldsymbol{x})\boldsymbol{\beta}_{\delta}$ (where $\boldsymbol{h}_{\delta}$ is a row vector and $\boldsymbol{\beta}_{\delta}$ is a column vector if we choose a parametric representation of the mean) and $c_{\delta}$ the covariance function of the discrepancy. We also denote $\boldsymbol{H}_{\delta}(\boldsymbol{X})$ the $n$ row matrix, the $i^{th}$ row of which is $\boldsymbol{h}_{\delta}(\boldsymbol{x}_i)$.\newline

@@

\begin{equation}
\mathcal{M}_4 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i}= F(\boldsymbol{x}_i,\boldsymbol{\theta})+\delta(\boldsymbol{x}_i)+\epsilon_i,
\label{eq:M3p}
\end{equation}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$, $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ and $\delta(\boldsymbol{x}_i)$ are two Gaussian
processes defined as before.
In their model, \citet{kennedy2001} also used a scale parameter $\rho$ in front of $F$.
This parameter is usually set to $1$ in many works  in order to achieve the best estimate on $\boldsymbol{\theta}$.
Thus, we omit this parameter in the model definition.
\newline

>>>>

\begin{eqnarray}
\mathcal{M}_2 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i} &=& F(\boldsymbol{x}_i,\boldsymbol{\theta}) + \epsilon_i,
\label{eq:M2}\\
F(\bullet,\bullet) & \sim &{\mathcal{GP}}{\Big(m_S(\bullet,\bullet),c_S\{(\bullet,\bullet),(\bullet,\bullet)\}\Big)},
\nonumber
\end{eqnarray}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$ and the random function $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ stands for a Gaussian process (GP) over the joint domain of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. For the following, we consider that the measurement error is independent from the error made by the Gaussian process. The mean function $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ is generally a linear form of simple functions of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. Its covariance function $c_S\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}=\sigma_S^2 r_{\boldsymbol{\psi}_S}\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}$ is such as the function $r_{\boldsymbol{\psi_S}}\{(\bullet,\bullet),(\bullet,\bullet)\}$ is the correlation function with a vector parameter $\boldsymbol{\psi}_S$. This parameter vector represents the scale and the regularity of the kernel and where $\sigma_S^2$ represents the variance. The mean $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ can be written as\newline

@@

where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$, and $\delta(\bullet)$ stands for a Gaussian process which mimics the discrepancy and will only depends on the input variables $\boldsymbol{x}$. For the rest of the article, we make the assumption that the discrepancy is independent from the measurement error. We can write $\delta(\bullet)\sim\mathcal{GP}(\boldsymbol{m}_{\delta}(\bullet),c_{\delta}(\bullet,\bullet))$ with $\forall \boldsymbol{x}, \ \boldsymbol{m}_{\delta}(\boldsymbol{x})={\boldsymbol{h}_{\delta}}(\boldsymbol{x})\boldsymbol{\beta}_{\delta}$ (where $\boldsymbol{h}_{\delta}$ is a row vector and $\boldsymbol{\beta}_{\delta}$ is a column vector if we choose a parametric representation of the mean) and $c_{\delta}$ the covariance function of the discrepancy. We also denote $\boldsymbol{H}_{\delta}(\boldsymbol{X})$ the $n$ row matrix, the $i^{th}$ row of which is $\boldsymbol{h}_{\delta}(\boldsymbol{x}_i)$.\newline

@@

\begin{equation}
\mathcal{M}_4 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i}= F(\boldsymbol{x}_i,\boldsymbol{\theta})+\delta(\boldsymbol{x}_i)+\epsilon_i,
\label{eq:M3p}
\end{equation}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$, $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ and $\delta(\boldsymbol{x}_i)$ are two Gaussian
processes defined as before. Similarly than before, we consider, for the following, that the measurement error, the discrepancy and the error induced by the surrogate are all independent.
In their model, \citet{kennedy2001} also used a scale parameter $\rho$ in front of $F$.
This parameter is usually set to $1$ in many works  in order to achieve the best estimate on $\boldsymbol{\theta}$.
Thus, we omit this parameter in the model definition.
\newline
